Fast algebraic filtering of surfaces from 3D medical images with Julia

### 2019-05-01 src/main.tex
added src dir

\begin{abstract}
In this paper we introduce a novel algebraic \textsc{lar-surf} filter, well founded on algebraic topology methods, to extract and smooth the boundary surface of any subset of voxels arising from the segmentation of a 3D medical image. The input is defined as a \emph{chain}, i.e.~as a vector from a linear space of 3-chains, represented in coordinates as a sparse Boolean array. The output is produced as the result of the mapping via the linear boundary operator $\partial_3:C_3 \to C_2$ between linear spaces of 3- and 2-chains.  In particular, when the input set of voxels is either not (4-)connected, or contains one or more empty regions inside, \textsc{lar-surf} generates a non connected set of closed surfaces, i.e.~a set of 2-cycles. The only data structures used are sparse arrays with one or two indices, i.e.~sparse vectors and matrices. This work is based on LAR (Linear Algebraic Representation) methods, and is implemented in Julia language, natively supporting parallel computing on hybrid architectures.
\end{abstract}

>>>>

\begin{abstract}
In this paper we introduce a novel algebraic \textsc{lar-surf} filter, well founded on algebraic topology methods, to extract and smooth the boundary surface of any subset of voxels arising from the segmentation of a 3D medical image. The input is defined as a \emph{chain}, i.e.~as a vector from a linear space of 3-chains, represented in coordinates as a sparse Boolean vector. The output is produced as the result of the mapping via the linear boundary operator $\partial_3:C_3 \to C_2$ between linear spaces of 3- and 2-chains.  In particular, when the input set of voxels is either not (4-)connected, or contains one or more empty regions inside, \textsc{lar-surf} generates a non connected set of closed surfaces, i.e.~a set of 2-cycles---using the language of algebraic topology. The only data structures used by this approach are sparse arrays with one or two indices, i.e.~sparse vectors and matrices. This work is based on LAR (Linear Algebraic Representation) methods, and is implemented in Julia language, natively supporting parallel computing on hybrid architectures.
\end{abstract}
